%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{University Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {International Islamic University Chittagong} % Organisation
    {Learning Management System (LMS)} % Project
    {Kumira, Chittagong} % Location
    {Jul 2022 - Jun 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {This was a team project, consisting two team member along with me. We build this online platform in two versions.}
        \item {\textbf{Version-1}: Raw Code of HTML, CSS and JS. \textbf{\href{https://cps-22.netlify.app/}{\textit{V1 Live Preview}}} || \textbf{Version-2}: Frame work of HTML,  CSS and JS. \textbf{\href{https://choloprogrammingshikhi.vercel.app/}{\textit{V2 Live Preview}}}}
        % \item {\textbf{Version-2}: Frame work of HTML,  CSS and Java Script. \textbf{\href{https://choloprogrammingshikhi.vercel.app/}{\textit{Project Live Preview}}}}
        \item {\textbf{Technical Skills:} Tailwind, Bootstrap, React, Node JS, Express JS, Database- MongoDB  and Software Testing, Git and GitHub.}
        \item {\textbf{Soft Skills:} Time Management, Teamwork, Project Lead and Management, Presentation skills, Report writing and Documentation.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Mentor-ship Project for Juniors} % Organisation
    {Twinkles Shopping Zone} % Project
    {Online Platform} % Location
    {Jan 2022 - Jun 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {While doing this project, I have learned new framework- PHP. \textbf{\href{https://sorowar-cse.github.io/Twinkles-Shopping-Zone-Full-Project/}{\textit{Project Live Preview}}}}
        \item {\textbf{Technical Skills:} Tailwind, Bootstrap, PHP, Local Database- Oracle  and Software Testing, Git and GitHub.}
        \item {\textbf{Soft Skills:} Time Management, Teamwork, Project Lead and Management, Presentation skills and Mentor-ship.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
   {International Islamic University Chittagong} % Organisation
    {Car Parking  Management} % Project
    {Kumira, Chittagong} % Location
    {Jan 2022 - Jul 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {I did the project during my 2nd semester as C++ Course project.  \textbf{\href{https://github.com/sorowar-cse/CPP-Project-Car_Parking_Management}{\textit{Project Code}}}}
        \item {\textbf{Technical Skills:} C++, Git and GitHub.}
        \item {\textbf{Soft Skills:} Time Management, Project Management, Presentation skills, Report writing and Documentation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
